---
title: "Han_02"
author: "Wanting Han"
date: "September 21, 2016"
output: html_document
---

#### 1a. Say “Vole vasopressin” 10 times as fast as you can. How many times did you trip up?

* Once.

#### 1b. What is the mean, median, sd, and interquartile range of the sample?

```{r sample, echo=TRUE}
library(magrittr)
library(dplyr)
vole_vaso <- c(98,96,94,88,86,82,77,74,70,60,59,52,50,47,40,35,29,13,6,5)
vole_mean <- mean(vole_vaso)
vole_median <- median(vole_vaso)
vole_sd <- sd(vole_vaso)
vole_IQR <- IQR(vole_vaso)
```

```{r results, echo=TRUE} 
vole_mean
vole_median
vole_sd
vole_IQR
```

#### 1c. What is the standard error of the mean (do this with a formula!)?

``` {r SE, echo=TRUE}
vole_n <- vole_vaso %>% length %>% sqrt
vole_se <- vole_sd/vole_n
vole_se
```

#### 1d. What does the standard error of the mean tell you about our estimate of the mean values of the population of vole vassopressin?

* Bigger sample sizes, less standard error of the mean, which means the sample estimation is closer to the population. 


#### 2a. Use sample() to get just one resample with a sample size of 10. What is its upper quartile?
``` {r resample, echo = TRUE}
vole_s10 <- 
  sample(vole_vaso, size = 10, replace = TRUE)
quantile(vole_s10, probs = 0.75)
```

### 2b. Build an initial data frame for simulations with the sample sizes 5 through 20. Have 100 simulations per sample size.
``` {r stim, echo = TRUE}
vole_df <- 
  data.frame(samp_size = rep(5:20, times = 100))
vole_df$sim <- 1:nrow(vole_df)
vole_df
```

#### 2c. Use this data frame to get simulated upper quartiles for each sample size.
``` {r quartitle, echo = TRUE}
vole_df_Q <- 
  vole_df %>%
  group_by(sim) %>%
  mutate(quantile = quantile(sample(vole_vaso, samp_size, replace = TRUE), probs = 0.75)) %>% ungroup()
vole_df_Q
```

### 2d. With a plot, make a guesstimate as to the best sample size for estimating the upper quartile of the population.
``` {r plot, echo = TRUE}
plot(quantile ~ samp_size, data = vole_df_Q, col = "red")
```

### 3a. With the upper quartile simulations, calculate the SD for each sample size using dplyr
```{r dplyr, echo = TRUE}
vole_df_SD <- 
  vole_df_Q %>% group_by(samp_size) %>% summarise(sd = sd(quantile)) %>% ungroup()
vole_df_SD
```

#### 3b. What does this value, the standard error of the upper quartile, mean?
* The standard error of the upper quartile shows how true the estimate of the upper quartile is.

#### 3c. What is the CI of the upper quartile with a sample size of 10. What does this mean?
``` {r CI, echo = TRUE}
vole_df_mean <-
  vole_df_Q %>% 
  group_by(samp_size) %>% 
  summarise(mean = mean(quantile)) %>%
  ungroup()
sd <- filter(vole_df_SD, samp_size == 10)
se <- sd[,2]/sqrt(10)
mean_10 <- vole_df_mean[6, 2]
upper_CI <- mean_10 + 2*se
lower_CI <- mean_10 - 2*se
upper_CI
lower_CI
```
* CI tells that there has 95% chance the upper quartile which calculated from sample size of 10 contains the true value of the population.

#### 3d. Extra Credit: Instead of having each sim calculate a upper quartile, and then sifting down to the SE of that upper quartile (or the CI), have each simulation calculate a CI. Then, for just a sample size of 10, how many CI’s contain the true value of 83?
``` {r}
vole_df_mean_sd <-
vole_df %>%
  group_by(sim) %>%
  mutate(mean = mean(sample(vole_vaso, samp_size, replace = TRUE)), sd = sd(sample(vole_vaso, samp_size, replace = TRUE))) %>% ungroup()

vole_df_mean_sd_10 <- filter(vole_df_mean_sd, samp_size == 10)

lower_CI <- vole_df_mean_sd_10[,3]-2*vole_df_mean_sd_10[,4]/sqrt(10)
upper_CI <- vole_df_mean_sd_10[,3]+2*vole_df_mean_sd_10[,4]/sqrt(10)
vole_df_CI <- bind_cols(lower_CI, upper_CI)
names(vole_df_CI) <- c("lower", "upper")

nrow(filter(vole_df_CI, lower<=83, upper>=83))
```
